Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-11-13 journal/ms.Rmd
minor corrections

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA is an important blueprint of both EXT and INT. If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.

@@

One possibility is that these patterns emerge from children’s use of statistical learning abilities [@saffran1996; @aslin2012; @smith2008]. The term "statistical learning" has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts. An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input. Previous work in the line of research has documented specific mechanisms which can explain the patterns found in the current study.

For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015]. According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semamtnic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without knowing the other words with witch they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

>>>>

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also compatible with INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT. If there is no such correlation, neither growth scenarios can be posited as a possible learning mechanism.

@@

One possibility is that these patterns emerge from children’s use of statistical learning abilities [@saffran1996; @aslin2012; @smith2008]. The term "statistical learning" has been used in the developmental literature to describes the process by which one acquires information about their environment through tracking the frequency distribution of some elements (e.g., words) in different contexts. An important property of this kind of learning is that it occurs without explicit instructions and through mere exposure to the input. Previous work in this line of research has documented specific mechanisms which can explain the patterns found in the current study.

For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015]. According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

### 2018-11-13 journal/ms.tex
minor corrections

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also compatible with INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlation between connectivity in the
end-state network and AoA is an important blueprint of both EXT and INT.
If there is no such correlation, neither growth scenarios can be posited
as a possible learning mechanism.

@@

One possibility is that these patterns emerge from children's use of
statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin,
\& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical
learning} has been used in the developmental literature to describes the
process by which one acquires information about their environment
through tracking the frequency distribution of some elements (e.g.,
words) in different contexts. An important property of this kind of
learning is that it occurs without explicit instructions and through
mere exposure to the input. Previous work in the line of research has
documented specific mechanisms which can explain the patterns found in
the current study.

For example, in the semantic domain, growth according to EXT can be
explained by a mechanism similar to cross-situational learning (Pinker,
2013; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this
mechanism, children track the co-occurrence of concrete nouns with their
possible semantic referents. The referent of a word heard in only one
naming situation can be ambiguous (e.g., when the word \enquote{ball} is
heard for the first time in the presence of both a ball and a chair),
but hearing the same word in a diversity of semantic contexts allows the
learner to narrow down the set of possible word-object mappings. In our
case, free association (used to determine semamtnic network
connectivity) is related to contextual co-occurrence (Fourtassi \&
Dupoux, 2013; Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that
highly connected words will tend to occur in a variety of speech and
referential contexts. This fact makes such words easier to learn because
they have more referential disambiguating cues across learning contexts.
Crucially, children can learn these words without knowing the other
words with witch they co-occur (hence the similarity with EXT). This
possibility is supported by the finding that words' diversity of
occurrence in child directed speech predicts their age of learning
(Hills et al., 2010).

>>>>

Connectivity in the global network is directly related to EXT as it
represents the explicit criterion this growth scenario uses to determine
what words should be learned first (Figure \ref{fig:growth}). Therefore,
a direct consequence of an EXT-like growth scenario is a correlation
between connectivity in the global network and the age of acquisition.
This correlation is also compatible with INT, although the causality is
reversed: higher connectivity in the global network is caused by earlier
learning, not the other way around. Some words end up being highly
connected in the global network precisely because they happen to be
acquired earlier and, therefore, have a higher chance of accumulating
more links over time. Thus, the correlation between connectivity in the
end-state network and AoA can result from both EXT and INT. If there is
no such correlation, neither growth scenarios can be posited as a
possible learning mechanism.

@@

One possibility is that these patterns emerge from children's use of
statistical learning abilities (Aslin \& Newport, 2012; Saffran, Aslin,
\& Newport, 1996; Smith \& Yu, 2008). The term \enquote{statistical
learning} has been used in the developmental literature to describes the
process by which one acquires information about their environment
through tracking the frequency distribution of some elements (e.g.,
words) in different contexts. An important property of this kind of
learning is that it occurs without explicit instructions and through
mere exposure to the input. Previous work in this line of research has
documented specific mechanisms which can explain the patterns found in
the current study.

For example, in the semantic domain, growth according to EXT can be
explained by a mechanism similar to cross-situational learning (Pinker,
2013; Smith \& Yu, 2008; Yurovsky \& Frank, 2015). According to this
mechanism, children track the co-occurrence of concrete nouns with their
possible semantic referents. The referent of a word heard in only one
naming situation can be ambiguous (e.g., when the word \enquote{ball} is
heard for the first time in the presence of both a ball and a chair),
but hearing the same word in a diversity of semantic contexts allows the
learner to narrow down the set of possible word-object mappings. In our
case, free association (used to determine semantic network connectivity)
is related to contextual co-occurrence (Fourtassi \& Dupoux, 2013;
Griffiths, Steyvers, \& Tenenbaum, 2007), meaning that highly connected
words will tend to occur in a variety of speech and referential
contexts. This fact makes such words easier to learn because they have
more referential disambiguating cues across learning contexts.
Crucially, children can learn these words without necessarily knowing
the meaning of all other words with witch they co-occur (hence the
similarity with EXT). This possibility is supported by the finding that
words' diversity of occurrence in child directed speech predicts their
age of learning (Hills et al., 2010).
